### 2019-12-09 README.Rmd
Prep for CRAN's requested patch, #290

EML is a widely used metadata standard in the ecological and environmental sciences. We strongly recommend that interested users visit the [EML Homepage](https://knb.ecoinformatics.org/#external//emlparser/docs/index.html) for an introduction and thorough documentation of the standard. Additionally, the scientific article *[The New Bioinformatics: Integrating Ecological Data from the Gene to the Biosphere (Jones et al 2006)](http://doi.org/10.1146/annurev.ecolsys.37.091305.110031)* provides an excellent introduction into the role EML plays in building metadata-driven data repositories to address the needs of highly heterogeneous data that cannot be easily reduced to a traditional vertically integrated database. At this time, the `EML` R package provides support for the serializing and parsing of all low-level EML concepts, but still assumes some familiarity with the EML standard, particularly for users seeking to create their own EML files. We hope to add more higher-level functions which will make such familiarity less essential in future development.

@@

This revision also supports the upcoming release of the EML 2.2 specification.

>>>>

EML is a widely used metadata standard in the ecological and environmental sciences. We strongly recommend that interested users visit the [EML Homepage](https://eml.ecoinformatics.org/) for an introduction and thorough documentation of the standard. Additionally, the scientific article *[The New Bioinformatics: Integrating Ecological Data from the Gene to the Biosphere (Jones et al 2006)](http://doi.org/10.1146/annurev.ecolsys.37.091305.110031)* provides an excellent introduction into the role EML plays in building metadata-driven data repositories to address the needs of highly heterogeneous data that cannot be easily reduced to a traditional vertically integrated database. At this time, the `EML` R package provides support for the serializing and parsing of all low-level EML concepts, but still assumes some familiarity with the EML standard, particularly for users seeking to create their own EML files. We hope to add more higher-level functions which will make such familiarity less essential in future development.

@@

This revision also supports the **[recently released EML 2.2.0 specification](https://eml.ecoinformatics.org/whats-new-in-eml-2-2-0.html)**.
